### 2013-01-14 draft.tex
save

\section*{Abstract}
{
%Как научная дисциплина компьютерное зрение является динамично развивающейся.
Computer vision is a dynamic scientific discipline.
%Одной из главных задач компьютерного зрения является слежение за объектом.
One of the most important objectives of the computer vision is real-time object tracking.
%Основой разрабатываемого алгоритма будет метод, предложенный Лукасом и Канаде.
A basis of the developed algorithm is the differential local method of Lucas and Kanade \cite{lucasKanade}.
%Данный метод позволяет отслеживать точечные особенности в последовательности кадров.
This method allows to keep track of point features in the frame sequence. 
The aim of this degree work is to develop a program that implements this functionality:
able to read a video-stream from a laptop's built-in camera,
in the presence of a human hand on the frame, program will display the number of unbent fingers.
%Но т.к. необходимо следить не за одной точечной особенностью, а за определенной группой точечных особенностей, то необходимо создать математическую модель кисти руки человека.
%И в дальнейшем отслеживать полученную математическую модель.
%Результатом будет программа, имеющая следующий функционал. 
%Возможность считывать видео-поток со встроенной камеры ноутбука.
%При присутствие на кадре человеческой ладони программу будет выводить количество несогнутых пальцев.
}

>>>>

\section*{Abstract}
{
%Как научная дисциплина компьютерное зрение является динамично развивающейся.
Computer vision is a dynamic scientific discipline.
%Одной из главных задач компьютерного зрения является слежение за объектом.
One of the most important objectives of the computer vision is real-time object tracking.
%Основой разрабатываемого алгоритма будет метод, предложенный Лукасом и Канаде.
A basis of the developed algorithm is the differential local method of Lucas and Kanade \cite{lucasKanade}.
%Данный метод позволяет отслеживать точечные особенности в последовательности кадров.
This method allows to keep track of point features in the frame sequence. 
The aim of this degree work is to develop a program that implements this functionality:
able to read a video-stream from a laptop's built-in camera,
in the presence of a human hand on the frame, program will display the number of unbent fingers.
%Но т.к. необходимо следить не за одной точечной особенностью, а за определенной группой точечных особенностей, то необходимо создать математическую модель кисти руки человека.
%И в дальнейшем отслеживать полученную математическую модель.
%Результатом будет программа, имеющая следующий функционал. 
%Возможность считывать видео-поток со встроенной камеры ноутбука.
%При присутствие на кадре человеческой ладони программу будет выводить количество несогнутых пальцев.
In this paper we presents a novel approach of hand identification and tracking by using a differential method for optical flow calculation developed by B. D. Lucas and T. Kanade \cite{lucasKanade}.
The proposed method consists of three steps which can be in real-time.
Firstly, in each frame we calculate contours and then point features using Harris corner detector \cite{harris_corner_detector}
}
